Exploring Molecular Conformations and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation

### 2013-08-04 writedown/npt-neq/alanine.tex
back up

\title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
\author{Han Wang}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
% \affiliation{Zuse Institute Berlin, Germany}
\author{Luigi Delle Site}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

@@

The molecular dynamics (MD) simulation has been proved to be useful in
understanding the behavior of a protein (or a short peptide segment)
in both static and oscilatatory electiric
fields~\cite{budi2005electric, budi2007effect, budi2008comparative,
  toschi2008effects, astrakas2011electric, astrakas2012structural,
  damm2012can, starzyk2013proteins, english2009nonequilibrium,
  solomentsev2012effects}. In these studies, the initial
configurations are usually taken from the Protein Data Bank (PDB).
And then the temperature controlled simulation are performed for from
a few to tens of nanoseconds, during which the interested
conformational chanages can be observed. Along the trajectories, the
secondary structure, root mean square displacement (RMSD), the dipole
moment and some shape parameters are calculated and investigated by
either plotted as a function of time, or doing time average over the
whole simulation. This approach release useful information on how the
secondary structure is changed by external electiric field.  However,
by plotting the quantities against time, one may observe strong
fluctuation in plots, which hintered the quantitative and conclusive
analysis on what is happening during the conformational change, when
it happens and what is the strength. Although the statistical
uncertainty in the time-averaged observations are small, the
time-average itself is not well defined for a nonequilibrium process
such as relaxing process to the new conformations under static
electiric field, and the dynamics under oscilatating electric field.

@@

In this paper, we firstly describe the idea of the D-NEMD, then
observables helping us the analyze the nonequilibrium properties
(i.e., the dipole moment, time-dependent properties of being a certain
conformation, the nonequilibrium transition properties and the net
property flux) are introduced. The numerical results of alanine
dipeptide under static and sine-shaped oscilatating electric field are
presented. By calculating the nonequilibrium properties from the D-NEMD
simulations, we are able to answer from which to which the conformation
changes, when do these changes happend, and how strong are the changes.
As far as we know, our simulation is the first D-NEMD simulation
on the electric field effect on alanine dipeptide, and provides new
information helping people better understand the nonequilibrium
effect of electric field on the protein conformation.

@@

\subsection{Nonequilibrium temperature control}

@@

\subsection{System settings and simulation protocol}
\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[]{fig.ala/fig-field-dipol.eps}
  \caption{The magnitude of the external electric field, and the
    x-component of the dipole moment of the alanine molecule as a
    function of time. The dashed lines are the strengths of the
    external electric field, while the solid lines are the dipole
    moments. Three test cases are indicated by different colors.}
  \label{fig:tmp3}
\end{figure}

@@

From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
metastable sets changes due to the external electric field, for
example, the population of conformations C vanishes in equilibrium,
but plays an important role when the electric field is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast is the change, and the relation to the speed of
the increasing electric field (i.e. the value of $t_{init}$). 
Firly, we study the population of the metastable conformations
Being more strict, we calculate the nonequilibrium observable
\begin{align}
  p_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
which is the time dependent probability of the alanine being in metastable
state $I$.
Secondly, we study the
forward and backward transition probability of the metastable conformations, which is defined by
\begin{align}
  P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
  P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
  % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
where $\Delta t$ is the time-scale of the observation.
For a revserible and homogeneous Markov process, it is easy to show
that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
process considered by the present work, this relation is genarlly not guarenteed. Finally, we study the backward net flux from metastable set $I$ to $J$:
\begin{align}
  F^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J).
\end{align}
Unlike the transition probabilities that are defined by the conditional
probability, the net flux is defined by the difference between
two joint probabilities, and prensents how much conformation $J$ is changed
into $I$ in the past $\Delta t$ interval. A positive value indicates the
flux from $J$ to $I$, while a negative value indicates a flux from $I$ to $J$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}
  \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
  \label{fig:tmp6}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta-mode2-010.eps}
  \includegraphics[]{fig.ala/fig-meta-mode2-040.eps}
  \includegraphics[]{fig.ala/fig-meta-mode2-200.eps}
  \caption{The populations of the metastable sets as a function of time.
    The dashed vertical lines indicate the three different time scale of
  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  \label{fig:tmp5}
\end{figure}

>>>>

\title{Exploring Molecular Conformations and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation}
% \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
\author{Han Wang}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
% \affiliation{Zuse Institute Berlin, Germany}
\author{Luigi Delle Site}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

@@

The molecular dynamics (MD) simulation has been proved to be useful in
understanding the behavior of a protein (or a short peptide segment)
in both static and oscillatory electiric
fields~\cite{budi2005electric, budi2007effect, budi2008comparative,
  toschi2008effects, astrakas2011electric, astrakas2012structural,
  damm2012can, starzyk2013proteins, english2009nonequilibrium,
  solomentsev2012effects}. In these studies, the initial
configurations are usually taken from the Protein Data Bank (PDB).
And then the temperature controlled simulation are performed for from
a few to tens of nanoseconds, during which the interested
conformational chanages can be observed. Along the trajectories, the
secondary structure, root mean square displacement (RMSD), the dipole
moment and some shape parameters are calculated and investigated by
either plotted as a function of time, or doing time average over the
whole simulation. This approach release useful information on how the
secondary structure is changed by external electiric field.  However,
by plotting the quantities against time, one may observe strong
fluctuation in plots, which hintered the quantitative and conclusive
analysis on what is happening during the conformational change, when
it happens and what is the strength. Although the statistical
uncertainty in the time-averaged observations are small, the
time-average itself is not well defined for a nonequilibrium process
such as relaxing process to the new conformations under static
electiric field, and the dynamics under oscillating electric field.

@@

In this paper, we firstly describe the idea of the D-NEMD, then
observables helping us the analyze the nonequilibrium properties
(i.e., the dipole moment, time-dependent properties of being a certain
conformation, the nonequilibrium transition properties and the net
property flux) are introduced. The numerical results of alanine
dipeptide under static and sine-shaped oscillating electric field are
presented. By calculating the nonequilibrium properties from the D-NEMD
simulations, we are able to answer from which to which the conformation
changes, when do these changes happend, and how strong are the changes.
As far as we know, our simulation is the first D-NEMD simulation
on the electric field effect on alanine dipeptide, and provides new
information helping people better understand the nonequilibrium
effect of electric field on the protein conformation.

@@

\subsection{Nonequilibrium temperature control}\label{sec:tmp2b}

@@

\subsection{System settings and simulation protocol}
\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[]{fig.ala/field.dipole/fig-field-dipol-conf.eps}
  % \\
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
  \caption{The magnitude of the external electric field, and the
    x-component of the dipole moment of the alanine molecule as a
    function of time. The dashed lines are the strengths of the
    external electric field, while the solid lines are the dipole
    moments. Three test cases are indicated by different colors.}
  \label{fig:tmp3}
\end{figure}

@@

From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
metastable sets changes due to the external electric field, for
example, the population of conformations C vanishes in equilibrium,
but plays an important role when the electric field is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast is the change, and the relation to the speed of
the increasing electric field (i.e. the value of $t_{init}$). 
Firly, we study the population of the metastable conformations
Being more strict, we calculate the nonequilibrium observable
\begin{align}
  P_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
which is the time dependent probability of the alanine being in metastable
state $I$.
% Secondly, we study the
% forward and backward transition probability of the metastable conformations, which is defined by
% \begin{align}
%   P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
%   P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
%   % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
% \end{align}
% where $\Delta t$ is the time-scale of the observation.
% For a revserible and homogeneous Markov process, it is easy to show
% that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
% process considered by the present work, this relation is genarlly not guarenteed.
Secondly,
we study the net probability flux from metastable set $I$ to $J$, defined by:
\begin{align}\label{eqn:tmp7}
  F_{J,I}(t) & =\lim_{\Delta t\rightarrow 0} \frac1{\Delta t} [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)].
\end{align}
which prensents the rate of how much conformation $J$ is changed
into $I$. A positive value indicates the
flux from $J$ to $I$, while a negative value indicates a flux from $I$ to $J$.
Now if project the proccess $\vect x_t$ onto the discretized states $\{A_1, A_2, B_1, B_2, C\}$. If the
project proccess is time-reversible, then it is obvious that
$ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
the irreversibility of the conformational change observed in the discretized space $\{A_1, A_2, B_1, B_2, C\}$.
In practive, to measure $ F_{J,I}(t)$, one need firstly approximate the limit
in Eq.~\eqref{eqn:tmp7} by finite difference, then the joint probabilities on
the right-hand-side can be calculated from the molecular trajectories.
If one wants a precise finite difference approximation, a smaller $\Delta t$ is
better, but then the statistical uncertainty of measuring the joint probabilities
is higher. We use a $\Delta t$ that is small enough for a precise finite difference
approximation, and not too small so that the joint probabilities can be measured
properly.
In the oscillating EF case, the net probability flux is also highly oscillating,
so it is convenient to study the integrated probability flux:
\begin{align}
  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
\end{align}
which presents the time averaged effect of the EF to the molecular conformation.

@@

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-5.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
  \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
  \label{fig:tmp6}
\end{figure}

@@

\subsection{Testing the finite-size effect}

@@

Just described in Sec.~\ref{sec:tmp2b}, we perform nonequilibrium MD
simulations in a finite size periodic system, and further divided it
into a Hamiltonian dynamics region and a thermostating region.
Since the periodic boundary condition and the division of the system
are artificial, 
we want to understand the finite-size effect of
these settings and the their influence to the simulation result.
Therefore, we
perform two additional simulations: one has box size $L=4.0$~nm and a
Hamiltonian dynamics region of radius $R_{ex} = 1.0$~nm, while the
other has box size $L=4.0$~nm and a Hamiltonian dynamics region of
radius $R_{ex} = 1.5$~nm, and compare them to the system
we used before, i.e. $L=2.7$~nm and $R_{ex} = 1.0$~nm.
Fig.~\ref{fig:tmp7} presents very good consistency of
the simulation results of the three systems, so the finite-size effect is
actually negligible in the system we used in the previous sections.

\section{Example II:
  periodically oscillating electric field}

We have tested the periodically oscillating electric field which has
a $\sin$-wave shape:
\begin{align}
  E(t) = E_0\sin(2\pi \omega t),
\end{align}
where $E_0$ is the strength of the field, which is chosen to be
1.0~V/nm.  $\omega$ is the frequency of the field, which is related to
the period $T$ by $\omega = 1/T$.  Here we tested three different
periods: 10, 40 and 200.  the periods of the later two are
commensurate to the time scales discovered by the nonequilibrium MD
simulation of constant electric field. The first is to test the if the
period is further reduced to smaller than 20~ps, there is any other
timescale of interest would play a role. Although the periods are
chosen according to the discovered time scales in the constant
electric field simulation, the nonequilibrium phenonema of oscillating
electric field cannot fully derived from the constant field system.
As far as the electric field changes, the internal time scale of the
system also changes, therefore, the nonequilibrium probabilities is a
complicated interplay of different internal time scales under
different electric fields. We do not try to theoretically predict
what will happen under the oscillating EF by a series constant EF simulation
revealing the internal dynamics under different strength of EF, but just directly
do the nonequilibrium MD simulation for the oscillating EF, and discuss
the observed phenonema.

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-mode2-dipol.eps}
  \caption{The nonequilibrium dipole moment of alanine dipeptide as a
    function of time. Only the $x$-component of the dipole moment is
    shown here. The black line: the static electric field with turning on
    time $t_{init} = 10$~ps. The red line: oscillating field with period
    10~ps. The green line: period 40~ps. The blue line: period 200~ps.}
  \label{fig:tmp8}
\end{figure}

Fig.~\ref{fig:tmp8} presents the $x$-component of the dipole moment as
a function of time. The red, green and blue lines stands for the
results of $T=10$~ps, 40~ps and 200~ps, respectively. The black lines
shows the dipole moment of constant electric field with
$t_{init}=10$~ps for reference. It demonstrates that for all periods
investigated, the alanine can adjust it's direction, which defined by
the direction of average dipole, according to the external electric
field almost immediately. At $T=200$~ps, the maximum magnitude of the
dipole moment is almost the same as the constant electric field, which
means that the changing of the electric field is so slow that the
alanine have enough time to fully relax the internal dipole. However,
for $T=40$~ps and $T=10$~ps, when the electric field changes faster,
although the molecules can align to the electric field immediately,
but it does not have enough time to relax the internal dipole, so we
see the maximum alanine's dipole moment reached is smaller for the shorter
period.

\begin{figure}
  \centering
  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0010.eps}
  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0040.eps}
  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0200.eps}
  % \includegraphics[width=0.49\textwidth]{fig.ala/fig-meta-mode2-2000.eps}
  \caption{ The probability of being in a certain metastable state for
    periodically oscillating electric field. Different periods,
    i.e. $T=10$~ps, 40~ps and 200~ps, are presented here.  The
    probability of being in a certain metastable state $I$, which is
    denoted by $P_I$ in this paper, is ploted by colored lines against
    time. The red line: $I = A_1$, the green line: $I = A_2$, the dark
    blue line: $I = B_1$, the pink line: $I = B_2$ and the light blue
    line: $I = C$. For $T=10$~ps and 40~ps, the nonequilibrium
    simulations of time 1000~ps are presented, while for $T=200$~ps,
    nonequilibrium simulations of tiem 3200~ps is presented.  }
  \label{fig:tmp9}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-5.eps}
  \caption{
    Integrated probability flux $Q_{J,I}(t)$ of the periodically
    oscillating EF is plotted against time. The unit of the
    time (horizontal axises) is picosecond.
    The integrated
    probability flux is defined by $Q_{J,I}(t) = \int_0^t F_{J,I}(\tau) d\tau$, where
    $F(t)$ is the net probability flux from metastable set $I$ to $J$.
    From up to down the rows present period 10, 40 and 200~ps, respectively.
    From left to right, the five
    columes show integrated flux $Q_{J,A_1}$, $Q_{J,A_2}$,
    $Q_{J,B_1}$, $Q_{J,B_2}$ and $Q_{J,C}$, respectively. In each plot,
    the red line stands for $J=A_1$, green for $J=A_2$, dark blue for $J=B_1$,
    purple for $J=B_2$ and light blue for $J=C$. In a certain time interval,
    if the integrated flux $Q_{J,I}$ increases, then there exist a (time-averaged)
    non-zero net flux from metastable set $I$ to $J$.
  }
  \label{fig:tmp10}
\end{figure}

The Fig.~\ref{fig:tmp9} shows the probability of being in a certain
metastable state for periodically oscillating electric field.  The
Fig.~\ref{fig:tmp10} presents the integrated probability flux of among
the metastable sets.
When the period is small, i.e. $T=10$~ps and
40~ps, the observed phenonema in the figures are basically the same.
The pobability in $A_1$, $A_2$, $B_1$ and $B_2$ does not change
too much with respect to time,
however, the probability in metastable set $C$ astonishingly
increase to approximately 0.17 for $T=10$~ps  and 0.27 for  $T=10$~ps.
Notice that in the constant EF case, although the dipole moment is
bigger than the  $T=40$~ps case (see Fig.~\ref{fig:tmp8}), the
probability of being in $C$ is indeed lower.  
The time needed to reach a steady state is
roughly 400~ps that is the same as the
constant EF case. Fig~\ref{fig:tmp10} shows some ever increasing
integrated probability fluxes, which imply some ever lasting and directional
flux among the metastable sets, see
Fig.~\ref{fig:tmp11} that presents a schematic plot of the probability
fluxes for $T=10$~ps. The probability flux of  $T=40$~ps is roughly
the same as $T=10$~ps, expect that
the flux from $B_2 $ to $A_1$ does not exist. 
This demonstrate a interesting phenonemon: the oscillating EF 
generates a directional probability flux among the metastable sets.
Moreover, some loops of the flux are detected: $A_1 \rightarrow B_1
\rightarrow B_2 \rightarrow A_2 \rightarrow A_1$, $A_1 \rightarrow B_1
\rightarrow B_2 \rightarrow A_1$,  $A_1 \rightarrow B_1
\rightarrow B_2 \rightarrow C \rightarrow A_1$ and $B_1
\rightarrow B_2 \rightarrow C \rightarrow B_1$.

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig.ala/graphs/graph-t0010.eps}
  \caption{The schematic plot of the main probability flux among the metastable
    states on the Ramachandran histogram
    for periodically oscillating EF, $T=10$~ps. The thickness 
    of the arrows approximately presnets the strength of the flux.
  }
  \label{fig:tmp11}
\end{figure}

When the period is $T=200$~ps, the phenonema are substentially different
from the high frequency cases ($T=10$ and 40~ps). Firstly, from Fig.~\ref{fig:tmp9}, the system reaches staedy state after around 2000~ps, while
Fig.~\ref{fig:tmp10} suggests an even long time scale, but we cannot draw
a very clear conclusion on it
due to the lack of computational power to perform even longer simulations. 
The steady probability of being in state $C$ is roughly the same as the
case of $T=40$~ps, although the maximum dipole moment is actually higher
than the latter. And the steady probability  of being in state $C$ is
also higher than the constant EF case, even the maximum dipole are roughly
the same. The time spend to reach the steady state is much longer than
the higher frequency cases, so this indicates a \emph{dynamically} longer time
scale in the system, comparing with the static EF case, in which all time scales
are actually decided by the \emph{static} external field. We also observe
a suden change in the probability flux from set $A_2$ to $A_1$ at
around 1600~ps, which may imply a \emph{dynamically} rare event.
Since we do not have the computer power to perform even longer simulations,
this hypothesis is not further checked.
